---
title: "Some simulations of the Prony systems"
author: "Andrey Akinshin"
date: "August 08, 2016"
output: html_document
---

```{r echo=F}
knitr::read_chunk('hyperbola.R')
```
```{r echo=F}
knitr::read_chunk('error-sets.R')
```

## Introduction

*(This section will be rewritten)*

Consider the following system of signals:
$$
  \mathcal{S} = \{(a, x), (b, y)\}, \quad a,b,x,y \in \mathbb{R}
$$
where $a$, $b$ are signal amplitudes and $x$, $y$ are signal positions.

Define the Prony map $\mathcal{P}$ as a map $\mathcal{P}: \mathcal{S} \mapsto (m_0, m_1, m_2, m_3)$ of the following form:
$$
  m_k = ax^k + by^k, \quad k = 0,1,2,3.
$$

Let $S_0 = \{(a_0, x_0), (b_0, y_0)\} \in \mathcal{S}$ be a so called reference signals: $a_0 = b_0 = 1, x_0 = 0, y_0 = h$ where h is a parameter which defines a distance between reference signals.

Let $\mathcal{S}_t = \{(a_t, x_t), (b_t, y_t)\} \subset S$ be a set of so called trial signals, $M_{min} \leq a_t, b_t \leq M_{max}; Z_{min} \leq x_t, y_t \leq Z_{max}$

Define a two-dimensional function $Q(x, y)$ as follows:
$$
  Q(x, y) = \min_{S_1 = \{(a_1, x), (b_1, y)\} \in \mathcal{S}_t} \textrm{Dist}(\mathcal{P}(S_0), \mathcal{P}(S_1))
$$
where $\textrm{Dist}$ is the Decart distance in the moment space.

### Hyperbolas

```{r hyperbola, message=F}
```

### Error sets

Let's write some R code for calculation value of $Q$ for $M_{min} = 0, M_{max} = 2, Z_{min} = -1, Z_{max} = 1$:

```{r error-sets, message=F}
```

---

## Figures

We will build all the plots for $h = \{0.1, 0.3, 0.5\}$:
```{r}
h <- c(0.1, 0.3, 0.5)
```

### Figure 1
Hyperbola $x_1 x_2 = -h^2$:
```{r}
drawHyperbola(h, -1)
```

### Figure 2

Error sets:
```{r fig.width=10}
drawErrorSet(h, sigma = 0)
```

### Figure 3
```{r fig.width=10}
drawErrorSet(h, sigma = 0.4)
```

### Figure 3.1
```{r fig.width=10}
drawErrorSet(0.3, sigma = 0.4, specific = data.frame(
  x = c(-0.14, -0.25, -0.31, -0.47), 
  y = c(0.31, 0.47, 0.14, 0.25), 
  h = c(0.3, 0.3, 0.3, 0.3)))
```

### Figure 5
Hyperbola $x_1 x_2 = h^2$:
```{r}
drawHyperbola(h, +1)
```